%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
%\usepackage[utf8]{inputenc}
\usepackage{multicol}
%\usepackage{csquotes}
\usepackage[margin=2.5cm]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{5cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\cfoot{\thepage\ of \pageref{LastPage}}


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Estelle} % Your first name
\familyname{Chasseloup} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{\Large{PhD Applicant}}
%\quote{\raggedleft Available from January 2017 \endgraf}%\\ Make your life an Eulerian graph}
\address{10 rue Gimelli}{83000 Toulon, France}
\mobile{+33681743798}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{estelle.chslp@gmail.com}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{Birth: 17 December 1991}
%\extrainfo{Single - Driving licence}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}
\maketitle
\section{Education}
\cventry{2014-2017}{MS, Pharmaceutical Sciences: Research in Pharmacokinetics
(three-year program)}{Université d'Aix-Marseille}{Marseille}{France}{}
\cventry{2014}{Special Diploma -- PK/PD Modeling and Simulation: Population
Approach}{Université d'Aix-Marseille}{Marseille}{France}{}
\cventry{2010-2014}{BS, Pharmaceutical Sciences}{Université d'Aix-Marseille}{Marseille}{France}{}

\section{Research Interests}
\cvline{}{%
\begin{itemize}
\item Pharmacometrics,
\item Clinical trial design optimization,
\item In-vitro In-vivo extrapolation,
\item Development of semi-mechanistic models.
\end{itemize}%
}

\section{Languages}

	\cventry{French}{Mother Tongue}{}{}{}{}
	\cvitemwithcomment{English}{\textbf{Independent User}.~ \textit{TOEIC score: 960/990}}{}{}{}
	\cvitemwithcomment{Italian}{\textbf{Basic User}.~~~~~~~~~~~~ \textit{B2 CEFR level}}{}{}{}
	\cvitemwithcomment{Spanish}{\textbf{Basic User}.~~~~~~~~~~~~ \textit{B1 CEFR level}}{}{}{}

\section{Professional Experiences}

\cventry{2017\\6 months}{Internship in PBPK}{Technologie Servier}{Orléans}{France}
{Software assessment - SimCYP, GastroPlus and PK-Sim.\\
\hspace*{1cm} $\rightarrow$ \textit{Advisor: Pharm.D. Magali Amiel.}}

	\cventry{2016\\6 months}{Internship in Clinical
	Pharmacokinetics}{Galderma}{Sophia Antipolis}{France}{Non compartmental
analysis, development of individual and population PK models for cutaneous
administration, model evaluation by bootstrapping visual predictive checks and
cross validation, individual simulations - Phoenix WinNonlin, NLME and R.\\
\hspace*{1cm} $\rightarrow$ \textit{Advisor: Dr. Khaled Benkali.}}

	\cventry{2015\\6 months}{Hospital Internship in Clinical
	Pharmacology}{APHM}{Marseille}{France}{External validation of a population PK model in
pediatrics - NONMEM and R.\\
\hspace*{1cm} $\rightarrow$ \textit{Advisor: Dr. Amélie Marsot.}}

	\cventry{2015\\3 months}{Internship in Pharmacometrics}{Hoffman-La
	Roche}{Basel}{Switzerland}{Development and evaluation of a population PK
model - NONMEM and R.\\
\hspace*{1cm} $\rightarrow$ \textit{Advisor: Dr. Valérie Cosson.}}

	%\cventry{2011-2014}{Discovery and application officinal internships - 10 weeks}{Pharmacie Vauban - Pharmacie du Théatre - Pharmacie de la Joliette}{Marseille and Toulon}{France}{}
\pagebreak

\section{Relevant Coursework}

\cventry{2016-2017}{M2 Research in Pharmacokinetics}{Prof. Joseph Ciccolini,
	Prof. Florence Gattacceca}{}{}{%
\begin{itemize}
	\item Modeling and Simulation: NLME and PBPK;
	\item Non-clinical and clinical drug development;
	\item Nanocarriers, analytical methods (RMN, IR, CPG, HPLC) and standard frameworks.
\end{itemize}%
}
\cventry{2014}{Special Diploma}{Prof. Athanassios Iliadis}{}{}{%
\begin{itemize}
\item Fundamental and usual PK models - Real process and model - Statistics,
Probability, Estimation.
\item Population approaches, modeling in research and development: non-linear
programming, simulation, dosage adjustement.
\item NONMEM, Phoenix WinNonLin NLME, Monolix, KineticPro and MATLAB.
\end{itemize}%
}

\section{Relevant Projects}
\cventry{2015-2016}{Hospital-University year}{Research option in Oncology
Pharmacochemistery}{}{}{
Development and assessment of new anti-cancer agents. Microwave-assisted synthesis
of quinazoline derivatives then cytotoxic (${IC}_{50}$ determination with MTT test) and anti-
invasive (cell escape test on fibronectin with speroids) properties assessment.
}
\cventry{2014-2015}{M1 Industry specialization}{Non-clinical drug development
option}{}{}{In-vitro study of inhibitory effect of erythromycin on CYP450 to assess
potential drug interactions.
\begin{itemize}
	\item Determination of erythromycin N-demethylase activity: turnover, $K_m$
		and $V_{\max}$ ;
	\item Inhibition study of various drug on CYP450 erythromycin N-demethylase activity and
ketoconazole $K_i$ determination;
\item Assessment of erythromycin in-vivo inhibiting power.
\end{itemize}%
}

\section{Skills on Softwares}

	\cventry{~}{NONMEM - Monolix - Phoenix WinNonLin NLME -
	KineticPro}{}{}{Exploratory analysis, non compartmental analysis,
individual and population PK modeling, dosage adjustment}{}
	\cventry{~}{R, MATLAB}{}{}{Data analysis, plots, basic programming}{}
	\cventry{~}{SimCYP, GastroPlus, PK-Sim}{}{}{Physiologically Based Pharmacokinetics modelling}{}
	%\cventry{~}{Phoenix WinNonLin - NLME}{}{}{Exploratory analysis, non compartmental analysis, individual and population PK modeling}{} %,goodness of fit plots, visual predictive checks, bootstrapping}{}	
	%\cventry{~}{KineticPro}{}{}{Individual and population PK modeling, dosage adjustment}{}
	%\cventry{~}{R}{}{}{Exploratory analysis, goodness of fit plots, visual predictive checks, data managment, Xpose and GGplot packages}{}
	%\cventry{~}{MATLAB}{}{}{Array calculus, matrix algebra, statistics, graphics, basic programming}{}

	%\cventry{NONMEM}{Approche de population PK/PD}{}{}{}{}{}
	%\cventry{Phoenix WinNonlin - NLME}{Approche de population PK/PD}{}{}{}{}
	%\cventry{Monolix}{Approche de population PK/PD}{}{}{}{}{}
	%\cventry{Pirana}{Plateforme de modélisation en Pharmacométrie}{}{}{}{}
	%\cventry{R}{Statistiques, Analyse exploratoire, Goodness of fit plots, Visual predictive checks, Gestion de bases de données}{}{}{}{}{}
	%\cventry{MATLAB}{Algèbre matriciel, Statistiques, Graphiques}{}{}{}{}
	%\cventry{Nonmat6}{Analyse de données}{Bibliothèque d'outils graphiques et numériques pour NONMEM}{}{}{}

	%\section{Pending Submissions}
	\section{Personal Interests}
\cvline{}{%
Hiking,
Problem solving,
Lifelong learning,
DIY.
}

	\section{References}
	\cventry{}{PharmD. Magali Amiel}{}{}{}{
Team leader DMPK at Technologie Servier.\\
\href{mailto:magali.amiel@servier.com}
{\textit{\emailsymbol magali.amiel@servier.com}}
	}
	\cventry{}{Prof. Florence Gattacceca}{}{}{}{
Professor in Pharmacokinetics, Université de Montpellier.\\
\href{mailto:florence.gattacceca@umontpellier.fr}
{\textit{\emailsymbol florence.gattacceca@umontpellier.fr}}
	}
	\cventry{}{Dr. Amélie Marsot}{}{}{}{
Research engineer in Pharmacometrics, APHM.\\
\href{mailto:amelie.marsot@ap-hm.fr}
{\textit{\emailsymbol amelie.marsot@ap-hm.fr}}
	}
	\cventry{}{Prof. Athanassios Iliadis}{}{}{}{
Professor Emeritus, Université d'Aix-Marseille.\\
\href{mailto:athanassios.iliadis@univ-amu.fr}
{\textit{\emailsymbol athanassios.iliadis@univ-amu.fr}}
	}

\end{document}
